The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add data pull for n individuals

source('../scripts/0-variables.R')
```

@@

### Network types and construction
We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (forest, forage, and open) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. 
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

>>>>

source('../scripts/0-variables.R')

DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```

@@

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and landcover). Two season
elementary-layers (winter and summer) and three landcover elementary-layers
(forest, forage, and open) combined for a total of six layers. Layers were
composed of individuals represented as nodes and social associations represented
as edges, for each season and landcover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
